---
title: "Tidy Text"
author: "Binyam Yilma"
date: "12/28/2020"
output: github_document
---

Setup
```{r}
library(tidyverse)
library(tidytext)

library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Get Data

```{r, cache = TRUE}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_reviews = 
  tibble(
    page = 1:100,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest(reviews) %>%
  mutate(review_num = row_number()) %>% 
  relocate(page, review_num)
```



## Do some tidy text stuff

Extracting words from the `text` field from the dynamite_reviews dataframe.
1 - can I extract the words? Yes.
```{r}

dynamite_words = 
  dynamite_reviews %>% 
  unnest_tokens(word, input = text) %>% 
  select(-urls)

```

2 - can I remove unnecessary words?


```{r}

```


```{r}

dynamite_words = 
  anti_join(dynamite_words, stop_words) # getting rid of stop words from our words - the anti-join here is saying, keep everything in this data frame that's not in the list of the "stop_words"

stop_words %>% View()

```


Usual tidyverse stuff ... 

```{r}

dynamite_words %>% 
  count(word, sort = TRUE) %>% 
  top_n(10) %>% 
  mutate(
    word = fct_reorder(word, n)
  ) %>% 
  ggplot(aes(y = word, x =n)) +
  geom_bar(stat = "identity")

```


# Compare across groups

Groups I want to compare are 1 star and 5 star reviews. 


How many words are coming out of 1 star reviews? 5 star reviews? 
```{r}
dynamite_words %>% 
  filter(stars %in% c(1,5)) %>% 
  group_by(stars) %>% 
    summarize (n = n())
```


Let's count words in these groups

What are the top 5 words that are appear the most 

```{r}

dynamite_words %>% 
  filter(stars %in% c(1, 5)) %>% 
  group_by(stars) %>% 
  count(word) %>% 
  top_n(5)
```

Now, let's say we're interested in something like: does the word "dumb" appear more often in 1 star reviews relative to 5 star reviews? So, this is where the "odds ratio"-esque thing comes in. 


We now need an "odds ratio"

```{r}
word_ratios = dynamite_words %>% 
  filter(stars %in% c(1, 5)) %>% 
  count(word, stars) %>% # we're going to focus on words that get used somehow frequently
  group_by(word) %>%  
  filter(sum(n) >= 5) %>% # focusing on words that appear at least 5 times 
  ungroup(word) %>% 
  pivot_wider(
    names_from = stars, 
    values_from = n, 
    names_prefix = "stars_",
    values_fill = 0
  ) %>% 
  mutate(
    stars_1_odds = (stars_1 + 1) / (sum(stars_1) + 1),
    stars_5_odds = (stars_5 + 1) / (sum(stars_5) + 1),
    log_OR = log(stars_5_odds / stars_1_odds) #high values of these means that the word appears more times in 5 stars than 1 stars; lower values than 0 means that the word appears more times in the 1 stars
  )
  
```


Can we do something useful with this ^^ ?

Trying to identify words that are more likely to happen in the 1 star reviews than 5 star reviews

```{r}

word_ratios %>% 
  mutate(
    pos_log_OR = ifelse(log_OR > 0, "5 star > 1 star", "1 star > 5 star")
  ) %>%
  group_by(pos_log_OR) %>% 
  top_n(10, abs(log_OR)) %>%  # getting the most extreme values of the pos_log_OR stuff
  ungroup() %>% 
  mutate(word = fct_reorder(word, log_OR)) %>% 
  ggplot(aes(y = word, x = log_OR, fill = pos_log_OR)) + 
  geom_bar(stat = "identity")


```


## Sentiment Analysis

Load lexicon

```{r}
bing_sentiments = get_sentiments("bing")
```


```{r}
dynamite_sentiments = inner_join(dynamite_words, bing_sentiments) %>% 
  count(review_num, sentiment) %>% 
    pivot_wider(
      names_from = sentiment, 
      values_from = n,
      values_fill = 0
    )  %>% 
    mutate(
      review_sentiment = positive - negative
    ) %>% 
    select(review_num, review_sentiment)
    
```



Combine with full data

```{r}

dynamite_sentiments = 
  left_join(dynamite_sentiments, dynamite_reviews) %>% 
    select(-urls)

```

Plot 

```{r}

dynamite_sentiments %>% 
  mutate(
    review_num = factor(review_num),
    review_num = fct_reorder(review_num, review_sentiment)
  ) %>% 
  ggplot(aes(x = review_num, y = review_sentiment, fill = stars)) + 
  geom_bar(stat = "identity") + 
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank()
  )

```


Can we look at positive and negative reviews

```{r}

dynamite_sentiments %>% 
  filter(review_sentiment == max(review_sentiment))

```

